---
title: " Lab Assignment 3"
author: "Mary Boateng"
date: "September 16,2025"
format: html
---

Import library and set working directory

```{r}
library(data.table)
getwd() # find address of  directory
setwd(getwd()) # set working directory to current directory
```

Read in the data

```{r}
data <-fread("heart_failure.csv")

```

## Section 1

Determine the unique elements for the `smoking` variable.

```{r}
unique(data$smoking)
```

## Section 2

Select all the observations for the `smoking` variable only.

```{r}
data[, .(smoking)] # select smoking variable only
```

## Section 3

Select all the observations only for those who do not smoke

```{r}
data[smoking == "No"] # select observations for non-smokers only
```

## Section 4

Select the observations in rows 100 through 110 and show only the `diabetes` and `smoking` variables.

```{r}
data[100:110, .(diabetes, smoking)] # select rows 100 to 110 for diabetes and smoking variables only
```

## Section 5

Select all the observations for those who smoked and died.

```{r}
data[smoking == "Yes" & death == "Yes"] # select observations for smokers who died
```

## Section 6

Select all the observations for those who were either female or who did not smoke or who has diabetes.

```{r}
data[sex == "female"|smoking =="No" | diabetes == "Yes"]
```
