---
title: "Lab Assignment 1"
author: "Mary Boateng"
date: "September 2, 2025"
format: html
editor: visual
---

# Section 1

Calculate the solution to the following five exercises.

## Q1: $$ 3\times 4 + 7 - 8 \div 13$$

```{r}
3 * 4 + 7 - 8 / 13
```

## Q2: $$e^{-3}$$

```{r}
exp(-3)
```

## Q3: $$\sqrt[4]{100}$$

```{r}
100^(1/4)
```

## Q4: $$ log_e(15.8)$$

```{r}
log(15.8)
```

## Q5: $$\sin\left(\frac{\pi}{6}\right)$$

```{r}
sin(pi / 6)
```

# Section 2

Why would the code produce an error?

x = 3

y = 2

x + Y

The code produces an error because R is case-sensitive, and the variable 'Y' is not defined. The correct variable name should be 'y' (lowercase) instead of 'Y' (uppercase). Therefore, the expression should be 'x + y' to avoid the error. Code can be fixed by defining both variables or matching the case of the variables.

## fixed code

```{r}
x=3
y=2
x+y
```

# Section 3

Create a vector of the sequence of values 3,5,7,...,19,21

```{r}
vec <- seq(3, 21, by = 2)
vec
```

# Section 4

Determine if the values in the lab_vector variable are numeric

```{r}
lab_vector <- c(3, 6, 3.141592654, 3 + 4i)
lab_vector
```

```{r}
is.numeric(lab_vector)
```

what does data type does the code `3 + 4i` produce?

```{r}
typeof(3 + 4i)
```

The code `3 + 4i` produces a complex number data type in R. The 'i' denotes the imaginary unit, so `3 + 4i` represents a complex number with a real part of 3 and an imaginary part of 4.

# Section 5

Create a vector of 100 values assigned to the variable `height`that rounds the values to one decimal place and is taken from a normal distribution with a mean $\large\mu = 172$, and a standard deviation, $\large\sigma = 10$.

```{r}
set.seed(123)  # Setting seed for reproducibility
height <- round(rnorm(100, mean = 172, sd = 10), 1)
height
```
